External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
\vspace{2mm}\\
\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
\vspace{-3mm}
\begin{equation}\label{equ7}\vspace{-3mm}
\begin{split}
&\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}_{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\\
&
s.t.
\quad
\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution \cite{pgpd} 
\vspace{-1mm}
\begin{equation}\label{equ8}\vspace{-1mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
\\
\textbf{Updating Internal Dictionary}: given the sparse coefficient vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ9} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
s.t.
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively. According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) 
has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ10}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
\end{equation}
The orthogonality of internal dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$. In Figure \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.

>>>>

We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
\vspace{2mm}\\
\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
\vspace{-3mm}
\begin{equation}\label{equ7}\vspace{-3mm}
\begin{split}
\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\end{split}
\end{equation}
Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}((\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|(\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m}|-\bm{\lambda},\mathbf{0}),
\end{equation}
where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eqn. (\ref{equ8}) can be found in the supplementary file.
\vspace{2mm}\\
\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ9} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
s.t.
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively. According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) 
has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ10}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
\end{equation}
The orthogonality of internal dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$. In Figure \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
